Fail Faster

### 2025-03-20 paper/paper.tex
blah

\section{Evaluation}
\label{section:eval}
% \jwc{Initial section here about eval}\tr{todo}
To assess the impact of our approach, we evaluate the performance and bug-finding speed of 
\name generators across a range of benchmarks. Our experiments compare generators 
built using our technique---with and without \csplitmix---against those implemented with 
existing generator libraries (and their default randomness mechanisms). Specifically, 
we implement 
two fully semantically 
equivalent staged generator libraries that replicate the behavior of \bq 
in OCaml and ScalaCheck in Scala, allows us to assess the effectiveness of our 
technique across different languages and runtime environments.

>>>>

\section{Evaluation}
\label{section:eval}
% \jwc{Initial section here about eval}\tr{todo}
To assess the impact of our approach, we evaluate the performance and bug-finding speed of 
\name generators across a range of benchmarks. Our experiments compare generators 
built using our technique---with and without \csplitmix---against those implemented with 
existing generator libraries (and their default randomness mechanisms). Specifically, 
we implement 
two fully semantically 
equivalent staged generator libraries that replicate the behavior of \bq 
in OCaml and ScalaCheck in Scala, allowing us to assess the effectiveness of our 
technique across different languages and runtime environments.
